CES analysis for Paul Brockway rebound paper

### 2015-09-25 Articles/Brockway_Rebound_2015/Brockway_2015.Rnw
Now creating a graph of Re vs. time.

<<sF-sK-graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=2.5, fig.cap="$sF$ and $sK$ values.", warning=FALSE>>=
ggplot(data=historicalData %>%
         melt(measure.vars = c("sF", "sK"),
              value.name = "value", variable.name = "variable")) + 
  geom_line(mapping = aes(x=Year, y=value, group=variable, linetype=variable)) +
  facet_grid(. ~ Country) +
  scale_x_continuous(breaks=c(1960, 1980, 2000)) +
  scale_y_continuous(breaks=c(0, 0.5, 1.0), limits=c(0, 1)) +
  xlab("") + 
  ylab("sF, sK") +
  xy_theme()
@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Resampling Calculations}
\label{sec:resampling_calculations}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Resampling Results}
\label{sec:resampling_results}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Calculate rebound by Equation~\ref{eq:rebound}.
%
\begin{equation} \label{eq:rebound}
  Re \approx 1 - \frac{\rho}{1 + \rho} = \sigma_{(kl)e}\; .
\end{equation}
%
<<calc_rebound>>=
# Add a Rebound column to the resample coefficients
resampleCoeffs <- resampleCoeffs %>%
  # Applying the approximation Re ~ 1 - rho/(1 + rho) = sigma
  mutate(Re = sigma) 
@
%
Plot resampling results for \Sexpr{nResamples} resamples in Figure~\ref{fig:rebound_graph}.
%
<<rebound_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=2.5, fig.cap="$\\alpha_e$ vs. $Re$ for all three countries.">>=
standardScatterPlot(data=resampleCoeffs, mapping=aes(Re, alpha_3), facet_formula=~Country, alpha=0.05, orig_color = "black") +
    # scale_x_continuous(limits=c(0, 5)) + 
    scale_x_log10(limits = c(0.001,100), breaks = c(0.01, 0.1, 1, 10), labels = c(0.01, 0.1, 1, 10)) +

@@

>>>>

<<sF-sK-graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=2.5, fig.cap="$sF$ and $sK$ values.", warning=FALSE>>=
ggplot(data=historicalData %>%
         melt(measure.vars = c("sF", "sK"),
              value.name = "value", variable.name = "variable") %>%
         mutate(
           Country = relevelFactor(as.factor(Country), countries),
           variable = relevelFactor(as.factor(variable), c("sK", "sF"))
         )
       ) + 
  geom_line(mapping = aes(x=Year, y=value, group=variable, linetype=variable)) +
  facet_grid(. ~ Country) +
  scale_x_continuous(breaks=c(1960, 1980, 2000)) +
  scale_y_continuous(breaks=c(0, 0.5, 1.0), limits=c(0, 1)) +
  xlab("") + 
  ylab("sF, sK") +
  xy_theme() +
  theme(legend.title=element_blank())
@

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Resampling}
\label{sec:resampling}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Rebound}
\label{sec:rebound_calculations}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%++++++++++++++++++++++++++++++
\subsection{Basic Rebound} 
\label{sec:basic_rebound}
%++++++++++++++++++++++++++++++

For the basic rebound calculations, 
we can calculate rebound by Equation~\ref{eq:rebound}.
%
\begin{equation} \label{eq:rebound}
  Re \approx 1 - \frac{\rho}{1 + \rho} = \sigma_{(kl)e}\; .
\end{equation}
%
<<calc_rebound>>=
# Add a Rebound column to the resample coefficients
resampleCoeffs <- resampleCoeffs %>%
  # Applying the approximation Re ~ 1 - rho/(1 + rho) = sigma
  mutate(Re = sigma) 
@
%
Plot resampling results for \Sexpr{nResamples} resamples in Figure~\ref{fig:rebound_graph}.

Note that the vertical axis is $\alpha_e$. We now know that this is the initial value for $\alpha_e$.
In fact, there would be a trajectory with each dot as its starting point.
%
<<rebound_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=2.5, fig.cap="$\\alpha_e$ vs. $Re$ for all three countries.">>=
standardScatterPlot(data=resampleCoeffs, mapping=aes(Re, alpha_3), facet_formula=~Country, alpha=0.05, orig_color = "black") +
    # scale_x_continuous(limits=c(0, 5)) + 
    scale_x_log10(limits = c(0.001,100), breaks = c(0.01, 0.1, 1, 10), labels = c(0.01, 0.1, 1, 10)) +

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Full rebound}
\label{sec:full_rebound}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Now, we calculate rebound by the full equation
%
\begin{equation} \label{eq:time_dependent_rebound}
  Re = 1 + \frac{s_F \left[ s_F (1 + \rho) + \rho \right] + \rho (s_F - 1 - s_k) + s_F }{(1 + s_k + s_F)(1 + \rho)}
\end{equation}
%
for each country.

<<Rebound, echo=TRUE>>=
Rebound <- leaf_apply(models, class = c("cesModel"), f = function(mod, id){
  # "id" is the Country for mod
  rho <- naturalCoef(mod)$rho
  historicalData %>% 
    filter(Country == id) %>%
    mutate(
      Re = 1 + 
              (sF * (sF*(1+rho) + rho) + rho*(sF - 1  - sK) + sF) / 
                    ( (1 + sK + sF ) * (1 + rho) )
      )
}) %>% 
  bind_rows() %>%
  mutate(
    Country = relevelFactor(as.factor(Country), rev(countries))
    )
@

<<Rebound-graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4.5, fig.cap="Time-dependent rebound.">>=
ggplot(Rebound) + 
  geom_line(mapping=aes(x=Year, y=Re, group=Country, linetype=Country)) +
  geom_hline(y=1, color = "gray70", size=0.3) +
  scale_y_continuous(breaks=c(0, 1, 2, 3), limits=c(0, 3)) +
  scale_linetype_manual(values = c(3,2,1)) +
  xlab("") +
  ylab("Rebound") +
  xy_theme() +
  theme(legend.title=element_blank())
@

If we want to do so, we could apply the same calculation to each resampled model,
which would give $n$ lines for each country in Figure~\ref{fig:Rebound-graph}.
This would be similar to Figure~9 in the CES paper.
